%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer} % Job title
    {Inari Agriculture} % Organisation
    {Cambridge, MA} % Location
    {Jan 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a cross-functional team of ML engineers and biologists to train a foundation LLM for plant genomes and fine-tune LoRA adapters for tissue-specific gene expression, achieving a 56\% accuracy gain and directly informing target prioritization for downstream gene editing experiments.}
        \item {Partnered with biologist stakeholders to design, deploy, and scale an in-house protein engineering platform in Airflow using AlphaFold and generative models, enabling rapid screening of proprietary CRISPR-Cas enzymes and eliminating a \$50k annual vendor subscription.}
        \item {Developed a high-throughput protein-protein interaction AlphaFold pipeline to pre-screen potential pathway interventions for trait improvement in soybean, reducing the number of candidates to be tested in the lab by 100x.}
        \item {Implemented a cross-species transfer learning pipeline using a modified variational autoencoder to leverage high-quality RNA sequencing data from well-studied species to augment sparser data in soybean, enabling more accurate gene regulatory network inference for target discovery.}
        \item {Developed a novel and robust method to extract quantitative physiological features from hundreds of noisy soybean root images using a combination of computer vision and network analysis methods.}
      \end{cvitems}
    }

    \cventry
    {Data Scientist} % Job title
    {} % Organisation
    {} % Location
    {Jan 2019 - Jan 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a high-throughput computational screen for estimating phenotypic impact of CRISPR-Cas edited alleles in plants using a mixture of protein language models and bioinformatic methods.}
        \item {Fine-tuned a protein language model to discover novel stability-enhancing mutations for improving CRISPR-Cas nuclease efficiency for genome editing in plants.}
        % \item {Developed epistasis-aware DNA and protein language models to score and prioritize high-impact deleterious mutations in sequenced corn varieties for correction via genome editing.}
        % \item {Supervised a team of co-op students to train a transformer-based \href{https://assets-eu.researchsquare.com/files/rs-1927200/v1_covered.pdf}{genomic foundation model in plants} to predict tissue-specific expression of edited genes.}
        \item {Spearheaded the application of deep learning for protein sequence-to-function modeling and gene regulatory network perturbation-response modeling, demonstrating its potential and leading to the establishment of a full ML/AI team.}
        \item {Mentored 10+ junior colleagues, interns, and data science co-op students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Fellow} % Job title
    {Insight Data Science} % Organisation
    {Boston, MA} % Location
    {Sept 2018 - Dec 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a \href{https://github.com/knowbodynos/wikontext}{Word2Vec model} to enhance Wikipedia page previews by displaying the most relevant information to the current page.}
        \item {Used Wikipedia's bi-directional clickstream data to validate a 17\% increase in relevance over default page previews.}
        \item {Built a \href{https://www.wikontext.us/}{Chrome browser extension} served using a jQuery/Flask/AWS stack to achieve high performance on real-time, client-side data.}
%        \item {\textbf{Technical Skills:} Python, Flask, JavaScript.}
%        \item {\textbf{Soft Skills:} Rapid prototyping, Teamwork.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Northeastern University} % Organisation
    {Boston, MA} % Location
    {Sept 2011 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {\textbf{Advisor:} Brent D. Nelson}
        \item {Designed a distributed algorithm using C++ and Python to systematically compute type-IIB string theory vacuum states on an HPC cluster.}
    		\item {Developed a custom Python-based load balancer optimized for distributed computing across multiple SLURM clusters with different resource constraints and usage patterns.}
        \item {Compiled the \href{http://rossealtman.com/toriccy/}{world's largest database} of 100k string theory vacua, resulting in discovery of candidate universes extending the Standard Model.} % (35 GB).
        \item {Estimated the number of vacua ($>10^{10,000}$) in the string landscape using deep neural networks using specialized ``equation learner'' layers.}
        \item {Built and maintained a \href{http://www.rossealtman.com/toriccy/}{queryable web UI} with MongoDB backend based on feedback from stakeholders in the string theory community.}
        \item {Co-founded the String Data group for ML applied to string theory, leading to international conferences and collaboration with industry.}
    %		\item {Trained and advised other researchers as a senior research group member.}
    %		\item {Coordinated with many collaborators across the US, Europe, Asia, and Africa.}
%        \item {\textbf{Technical Skills:} Python, Keras, MongoDB, High-performance computing.}
%        \item {\textbf{Soft Skills:} Independent Research, Scientific Communication.}
      \end{cvitems}
    }

%%---------------------------------------------------------
%  \cventry
%    {Graduate Research Assistant} % Job title
%    {Rensselaer Polytechnic Institute} % Organisation
%    {Troy, NY} % Location
%    {Sept 2010 - May 2011} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item \textit{Advisor:} Shengbai Zhang
%        \item {Researched the band gap properties of photovoltaic materials for use in improved solar cells.}
%        \item {Investigated the unusual band gap properties of chalcopyrite (CuFe${\rm S}_{2}$).}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Graduate Research Assistant} % Job title
%    {Cornell University} % Organisation
%    {Ithaca, NY} % Location
%    {Sept 2009 - May 2010} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item {\textit{Advisor:} Richard V. E. Lovelace}
%        \item {Authored code to simulate realistic stellar occultations, generate corresponding ground intensity data, and recover amplitude and phase data.}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Undergraduate Research Assistant} % Job title
%    {Cornell University} % Organisation
%    {Ithaca, NY} % Location
%    {June 2007 - August 2007} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item {\textit{Advisor:} Saul Teukolsky}
%        \item {Co-authored code for an ongoing project to simulate comptationally difficult relativistic astronomical scenarios such as binary black hole systems.}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Research Intern} % Job title
%    {Stony Brook University} % Organisation
%    {Stony Brook, NY} % Location
%    {June 2003 - May 2005} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item {\textit{Advisor:} Nancy Goroff}
%        \item {Authored code to interface with MacroModel conformation calculations and determine the energetically stable states of complex macromolecules.}
%        \item {Investigated most energetically favorable techniques for constructing kekulene on a cyclodextrin scaffold.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
